---
title: "Lab 7 Rank Based Tests"
author: "Sara Orofino"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Hey Andrew - here we go again! Glad you're along for this journey with me. 

```{r, echo = FALSE}
library(tidyverse) 

kermit <- read_csv("kermit.csv")

```

Sara, I'm beginning to doubt your commitment to our code.

I'm not much of a commitment girl but for you Andrew I can make this thing work.

<<<<<<< HEAD
 
=======

If you are the collaborator:
-load the tidyverse
-read in the kermit data as "kermit"
-make some side-by-side histograms of the Score.pre for all respondents, separated by the gender column.

```{r}

kermit_hist <- ggplot(kermit, aes(x = Score.pre))+
  geom_histogram(bins = 4)+
  facet_wrap(~Gender)

kermit_hist

```

Creator: Perform rank-based comparisons using Mann-Whitney U and Wilcoxon-Signed Rank

Question: Is there a significnat difference in pre-talk ranks of Kermit for Male and Female respondents? 

```{r}
#H0: No significant difference in ranks between male and female respondents
#HA: There is a significant difference in ranks between male and female respondents 

mwu_kermit <- kermit %>% 
  wilcox.test(Score.pre ~ Gender, data = .)

mwu_kermit

# Retain the null p-value = 0.4001
```
"There was no significant differencein ranks for male and female respondents (W = 155.5, p = 0.40, alpha = 0.05"
